Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-30 paper/main.tex
rewrite introduction to applications

In this section we apply the previously developed methods to the problem of parameter estimation
of our model.
We cover 3 distinct cases with increasing level of complexity.
In the first study, we utilize results previously obtained by Amir et. al~\cite{Amir2014,Amir2014_2}
who investigated elastic deformations of \ac{ecoli} that are partially trapped within a narrow
tube and subject to a force resulting from a fluidic flow.
This setup does not involve any cell-cell interactions but specifically requires a flexible rod.
It is therefore well suited as a starting point to assess the usefulness of our methods and the
ability of our model to describe these results.\\
The last two cases consider time-series of microscopic images containing multiple cells (see
subsection~\ref{section:application-2}) which will be used to perform a parameter estimation of our
full mechanical model.
The approach is split into a first part which considers a time interval that does not contain any
division events and a second part which extends the initially chosen interval to include division
events.
In the first part, we cover a time interval which does not contain division events and thus utilize
the direct comparison algorithm while the second case contains division events and in turn requires
usage of the image-space metric.

>>>>

In this section we apply the previously developed methods and model to three case-studies, each
increasing in complexity.
We set out to estimate the parameters of every configuration.

First, we fit our model to data of elastically bending bacteria confined in a microfluidic
apparatus which was previously published by Amir et. al~\cite{Amir2014,Amir2014_2}.
This scenario isolates the mechanics of the flexible rod and is void of any complex cell-cell
interactions.
It is therefore well suited as a starting point in assessing the fidelity of our approach.

Subsequently, we extend our scope by incorporating multiple bacteria with cell-cell interactions
(see subsection~\ref{section:application-2}).
Initially, we consider a time interval that does not contain division events and are thus able to
employ the direct metric (see \nameref{subsec:direct-metric}).
Finally, we apply the image-space metric (see \nameref{subsec:image-space-metric}) to a time-series
containing multiple division events, demonstrating the feasibility of our approach in such
scenarios.
